--- 
title: "BSL-23"
author: "Halliwick PD Unit"
date: "`r format(Sys.time(), '%d %B, %Y @ %H:%M')`"
output: pdf_document
classoption: x11names
header-includes:    
    - \usepackage{longtable}
    - \usepackage{booktabs}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{lscape}
    - \newcommand{\blandscape}{\begin{landscape}}
    - \newcommand{\elandscape}{\end{landscape}}     
---

\pagenumbering{gobble}

```{r setupVariables, include=FALSE}
### Variables:

linePath = TRUE
lineSmooth = FALSE
showStdError = FALSE
spanValue = 0.3

# some global variables get set after libraries are loaded and data received 
```

```{r setupLibraries, code=readLines("libraries.R"), echo=F, warning=F, error=F, message=F}
```

```{r setupFunctions, code=readLines("functions.R"),echo=F, warning=F, error=F, message=F}
```

```{r getData, code=readLines("getData.R"), echo=F, warning=F, error=F, message=F}
# gets data from Limesurvey based on .properties file
```

```{r cleanData, code=readLines("cleanData.R"), echo=F, warning=F, error=F, message=F}
# cleans data:
#   - sets data types
#   - changes column names if necessary
#   - deals with missing values, if necessary
#   - filters data and selects necessary columns
```

```{r makePlots, echo=F, warning=F, error=F, message=F}

internalData <- mainData %>% 
  select(submitdate,starts_with('ISQ')) %>% 
  mutate(submitdate = as.Date(submitdate)) %>% 
  pivot_longer(cols = starts_with('ISQ')) %>% 
  group_by(submitdate) %>% 
  summarise(AinternalMean = round(mean(value),3)) %>% 
  pivot_longer(AinternalMean,values_to = "score",names_to = "measure")
               

impulseData <- mainData %>% 
  select(submitdate,starts_with('BEQ')) %>% 
  mutate(submitdate = as.Date(submitdate)) %>% 
  pivot_longer(cols = starts_with('BEQ')) %>% 
  group_by(submitdate) %>% 
  summarise(CimpulseMean = round(mean(value),3)) %>% 
  pivot_longer(CimpulseMean,values_to = "score",names_to = "measure")

pStateData <- mainData %>% 
  select(submitdate, starts_with('PSQ')) %>% 
  mutate(submitdate = as.Date(submitdate)) %>% 
  rename(BpersonalScore = starts_with('PSQ24')) %>% 
  pivot_longer(BpersonalScore,values_to = "score",names_to = "measure")

joinedData <- union(internalData,impulseData) %>% 
  union(.,pStateData)


param_names <- c(
                `AinternalMean` = "1. Internal Stress Level",
                `CimpulseMean` = "3. Impulsive Behaviour Level",
                `BpersonalScore` = "2. Overall Personal Feeling State"
                )


plot.BSL <- ggplot(joinedData, aes(x = submitdate, y = score)) +
  geom_line() + 
  geom_point() +
  facet_wrap(~ measure, ncol = 1, scales = 'free_y', labeller = as_labeller(param_names)) +
  labs(x="Time",y="Scores", title = "BSL scores over time") +
  theme_gdocs()


```

The BSL-23 questionnaire is an instrument designed to track main BPD related factors over time on _weekly basis_. There are 3 scales in BSL-23:

* **Internal Feeling Level** - characterizes the $\color{violet}{\emph{\text{stress/strain}}}$ level due to the thoughts and feelings characteristic of BPD. Maximal score is **4** and minimal is **0**. Lower score is better; _downward_ trend in the timeline suggests an improvement.
* **Overall Feeling State** - characterizes the $\textcolor{teal}{\emph{\text{overall personal  feeling  state}}}$ - how you felt overall for the last week. Maximal score is **100** and minimal is **0**. Higher score means feeling better; _upward_ trend in the timeline suggests an improvement.
* **Impulsive Behaviour Level** - this characterizes the $\color{magenta}{\text{\emph{impulsive  behaviour}}}$  level characteristic of BPD. Maximal score is **4** and minimal is **0**. Lower score is better; _downward_ trend in the timeline suggests an improvement.

\vspace{5mm}

```{r PlotBSL, echo=F, warning=F, error=F, message=F}
plot.BSL

```
